\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed

### 2014-10-08 Paper/grass.tex
Cite Ghisalberti and Nepf, 2006 as reference for rigid dowels

The instability and the resulting flow structures persist in lab experiments even when flexible grass mimics are replaced by rigid dowels \cite{Ghisal02}. 

@@

The vegetation, assumed dense, exerts a drag modeled by a continuous body force $\mathbf{f}$.
% We assume the vegetation to be dense and model the drag by a continuous body force $\mathbf{f}$.
This drag enters the fluid mass and momentum balance equations as 
\begin{equation}
\quad \grad\cdot\bu = 0,\hspace{3mm} \rho \left(\bu_{t}+\bu.\grad\bu \right) = -\grad p+\mu\grad^{2}\bu +\mathbf{f}+\rho\mathbf{g}
\label{navier-stokes}
\end{equation}
where $\rho$ is the fluid density, $\mathbf{u}$ the velocity, 
$p$ the pressure, $\mu$ the eddy viscosity (the flow is turbulent) and $\mathbf{g}$ the acceleration due to gravity. 
The Reynolds number of the flow based on the scale of the grass blade is $O(10^2-10^3)$; therefore, neglecting the skin friction, we model it based on the form drag on the vegetation, $\mathbf{f}=N_g C_N \rho u^{2}d\bx$, where  $N_g$ is the blade number density per unit horizontal area, $C_{N}$ the drag coefficient, and $d$ the average blade width projected perpendicular to the flow. 
% We model it as 
% $\mathbf{f_{d}}=C_N \rho u_{N}^{2}d\bn$, 
% where $d$ is the average width of grass blade projected in the flow direction, $C_{N}$ the drag coefficient, and $u_{N}$ and $\bn$ are the velocity component and unit vector normal to the grass (see fig.~\ref{basicflow} for a schematic). 
In the field, both $C_N$ and $N_g$ vary with position, but we do not expect these variations to be central to the instability mechanism, and therefore take $C_N$ and $N_g$ to be constants. 
Based on previous experiments \cite{Vivoni98,Nepf00}, we take $C_N \approx 1$.
\newline
\begin{figure*}
 \includegraphics{SetAll_imgsc}
%\end{figure}
%\begin{figure*}
%\begin{tabular}{cccc}
%{\includegraphics[height = 4cm, width = 5.8cm]{Set4_dens28_imgsc}} &
%{\includegraphics[scale = 0.67]{Set4_dens30_imgsc}} &
%{\includegraphics[height = 4cm,width = 5.8cm]{Set4_dens32_imgsc}} &
%{\includegraphics[height = 4.15cm,width=6.5cm]{Set4_dens34_imgsc}} \\
%{\includegraphics[height = 4cm, width = 5.8cm]{Set5_dens38_imgsc}} &
%{\includegraphics[scale = 0.67]{Set5_dens40_imgsc}} &
%{\includegraphics[height = 4cm, width = 5.8cm]{Set5_dens42_imgsc}} &
%{\includegraphics[height = 4.15cm,width=6.5cm]{Set5_dens46_imgsc}} \\

>>>>

The instability and the resulting flow structures persist in lab experiments even when flexible grass mimics are replaced by rigid dowels \cite{Ghisal02,Nepf06}. 

@@

The vegetation, assumed dense, exerts a drag modeled by a continuous body force $\mathbf{f}$.
% We assume the vegetation to be dense and model the drag by a continuous body force $\mathbf{f}$.
This drag enters the fluid mass and momentum balance equations as 
\begin{equation}
\quad \grad\cdot\bu = 0,\hspace{3mm} \rho \left(\bu_{t}+\bu.\grad\bu \right) = -\grad p+\mu\grad^{2}\bu +\mathbf{f}+\rho\mathbf{g}
\label{navier-stokes}
\end{equation}
where $\rho$ is the fluid density, $\mathbf{u}$ the velocity, 
$p$ the pressure, $\mu$ the eddy viscosity (the flow is turbulent) and $\mathbf{g}$ the acceleration due to gravity. 
The Reynolds number of the flow based on the scale of the grass blade is $O(10^2-10^3)$; therefore, neglecting the skin friction, we model it based on the form drag on the vegetation, $\mathbf{f}=N_g C_N \rho u^{2}d\bx$, where  $N_g$ is the blade number density per unit horizontal area, $C_{N}$ the drag coefficient, and $d$ the average blade width projected perpendicular to the flow. 
% We model it as 
% $\mathbf{f_{d}}=C_N \rho u_{N}^{2}d\bn$, 
% where $d$ is the average width of grass blade projected in the flow direction, $C_{N}$ the drag coefficient, and $u_{N}$ and $\bn$ are the velocity component and unit vector normal to the grass (see fig.~\ref{basicflow} for a schematic). 
In the field, both $C_N$ and $N_g$ vary with position, but we do not expect these variations to be central to the instability mechanism, and therefore take $C_N$ and $N_g$ to be constants. 
Based on previous experiments \cite{Vivoni98,Nepf00}, we take $C_N \approx 1$.
\newline
\begin{figure*}
 \includegraphics{SetAll_imgsc_hsv}
%\end{figure}
%\begin{figure*}
%\begin{tabular}{cccc}
%{\includegraphics[height = 4cm, width = 5.8cm]{Set4_dens28_imgsc}} &
%{\includegraphics[scale = 0.67]{Set4_dens30_imgsc}} &
%{\includegraphics[height = 4cm,width = 5.8cm]{Set4_dens32_imgsc}} &
%{\includegraphics[height = 4.15cm,width=6.5cm]{Set4_dens34_imgsc}} \\
%{\includegraphics[height = 4cm, width = 5.8cm]{Set5_dens38_imgsc}} &
%{\includegraphics[scale = 0.67]{Set5_dens40_imgsc}} &
%{\includegraphics[height = 4cm, width = 5.8cm]{Set5_dens42_imgsc}} &
%{\includegraphics[height = 4.15cm,width=6.5cm]{Set5_dens46_imgsc}} \\
